Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-28 paper.tex
new pdf build, change PWR into LWR
final read

The relative uncertainty of the uranium consumption dedicated to \gls{PWR}
\gls{UOX} fuel fabrication starts at about $7\%$, slowly dropping from year 20
to 100 and stabilizing around $3\%$ after year 100.

Fluctuation of the full relative uncertainty can be observed before year 50.
Those fluctuation are induced by the fuel loading: all reactors at the beginning
of the simulation have synchronized fuel cycles, reloading in the same time
step.  This phenomenon disappears with the gradual decommissioning of the
initial reactors, spread over 50 years.

@@

The uncertainty contribution from the cycle length between year 40 and 70 comes
mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
years this contribution follows the thermal power contribution closely,
suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
mechanism of this contribution, the variation of cycle length being driving a
direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
Both the fuel enrichment and separation efficiency showed a relative
contribution smaller than $0.4\%$.

Around the year 70, the relative uncertainty related to cycle time is slightly
bigger than the overall relative uncertainty. This effect is related to the
\gls{OFAT} method used to estimate the individual uncertainty contribution.
While allowing a quick access to the individual contribution, the \gls{OFAT}
method does not capture coupling effect between the different parameters.

@@

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Nevertheless such conclusions are constrained by the simulation
hypothesis: not considering radioactive decay removes the decay of $^{241}$Pu
during cooling and considering a transition to fast reactors minimizes the
impact of the discharge composition change induced by the cycle length
variations, when reprocessing them to build the next \gls{MOX} fuel batch.

@@

Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
assess the individual contribution of each parameter, missing all the coupling
effects between them...

>>>>

The relative uncertainty of the uranium consumption dedicated to \gls{LWR}
\gls{UOX} fuel fabrication starts at about $7\%$, slowly dropping from year 20
to 100 and stabilizing around $3\%$ after year 100.

Fluctuation of the full relative uncertainty can be observed before year 50.
Those fluctuations are induced by the fuel loading: all reactors at the beginning
of the simulation have synchronized fuel cycles, reloading in the same time
step.  This phenomenon disappears with the gradual decommissioning of the
initial reactors, spread over 50 years.

@@

The uncertainty contribution from the cycle length between year 40 and 70 comes
mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
years this contribution follows the thermal power contribution closely,
suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
mechanism of this contribution, the variation of cycle length driving a
direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
Both the fuel enrichment and separation efficiency showed a relative
contribution smaller than $0.4\%$.

Around the year 70, the relative uncertainty related to cycle time is slightly
bigger than the overall relative uncertainty. This effect is related to the
\gls{OFAT} method used to estimate the individual uncertainty contribution.
While allowing a straightforward estimate of the individual contribution, the \gls{OFAT}
method does not capture coupling effects between the different parameters.

@@

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Nevertheless such conclusions are specific to this particular scenario
definition: not considering radioactive decay removes the decay of $^{241}$Pu
during cooling, and a transition to fast reactors minimizes the
impact of the change in discharge composition induced by the cycle length
variations when reprocessing spent fuel to build the next \gls{MOX} fuel batch.

@@

Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
assess the individual contribution of each parameter, missing all the coupling
effects between them.
